Fluent statistical computing interfaces for biological data analysis

### 2020-03-13 Rmd/01-intro.Rmd
words etc.

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all it’s messes and 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process involving computation and visualization,
leading to new hypotheses that can be tested and formalised using 
statistical modelling. As datasets grow in complexity and become
increasingly heterogeneous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs. This is certainly true in high-throughput biological 
data analysis, where constraints on computation time and memory, in addition
to the analyst's time, results in EDA becoming increasingly difficult and 
neglected.

>>>>

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all it’s messes and 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process involving computation and visualization,
leading to new hypotheses that can be tested and formalised using 
statistical modelling. As datasets grow in complexity and become
increasingly heterogeneous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs. This is certainly true in high-throughput biological 
data sceince, where constraints on computation time and memory, in addition
to the analyst's time, results in EDA becoming increasingly difficult and 
neglected.

This thesis develops tools and frameworks to perform EDA as part of the
biological data science workflow...
